### 2018-04-29 paper/evaluation.tex
don't add figures twice -- it's cheating

To evaluate \name, we take interest in users owning a variable amount of devices of different types, and frequently switching among them.
To the best of our knowledge, there exists no real-world dataset of the devices connection times of such a user.
We have thus implemented an evaluation testbed where each user's behavior is simulated  according to the following properties:
\begin{itemize}
	\item The user owns a variable amount of devices (3 to 10). We consider the following device types: mobile (e.g. tablet, phone), portable (laptop), fixed (workstation, home computer) and server (such as a NAS, Raspberry Pi or rented appliance);
	\item She can travel between different locations, say her home, her workplace and and outside;
	\item She makes a different use of her devices depending on her location: her home computer will only be accessed at home, while her phone can be accessed everywhere (though she tends to use it the most at home, for instance).
\end{itemize}

We thus model each user with a Hidden Markov Model, as presented in section~\ref{sub:a_model_of_the_user_s_behavior}.
We keep the different possible locations $\mathcal{L}$ to a number of three, and generate different state transition matrices $A$ and emission probability matrices $B$ for each user.

$B_{*, d}$, the probability that device $d$ is used in each location, depends on $d$'s device type:

\begin{itemize}
	\item for each location, every mobile device $d_m$ has a random but high probability of being online: $\forall l \in \mathcal{L}, B_{l, d_m} \in [0.6, 1]$;
	\item a portable device $d_p$ has a much lower probability of being used ($\forall l \in \mathcal{L}, B_{l, d_p} \in [0.2, 0.8]$); 
	\item a fixed appliance $d_f$ has a non-zero probability of usage in only one location: $\exists l \in \mathcal{L}, \forall l' \neq l, B_{l, d_f} \in [0.4, 0.8] \& B_{l, d_f} = 0$
	\item a server $d_s $has a very high probability of working, 
\end{itemize}

@@

$$A =
\kbordermatrix{
      & W            & O            & H            \cr
    W & \sfrac{2}{3} & \sfrac{1}{3} & 0            \cr
    O & \sfrac{1}{3} & \sfrac{1}{3} & \sfrac{1}{3} \cr
    H & 0            & \sfrac{1}{3} & \sfrac{2}{3} \\[0.3em]
}, \;
B = 
\kbordermatrix{
      & W     & O   & H   \cr
    p & 0.7 & 0.6 & 0.8 \cr
    w & 0.7 & 0   & 0   \cr
    h & 0   & 0   & 0.7 \cr
    l & 0.2 & 0.4 & 0.6 \\[0.3em]
}$$

@@

>>>>

To evaluate \name, we take interest in users owning a variable amount of devices of different types, and frequently switching among them.
To the best of our knowledge, there exists no real-world dataset of the devices connection times of such a user.
We have thus implemented an evaluation testbed where each user's behavior is simulated  according to the following properties:
\begin{itemize}
	\item The user owns a variable amount of devices. We consider the following device types: mobile (e.g. tablet, phone), portable (laptop), fixed (workstation, home computer) and server (such as a NAS, Raspberry Pi or rented appliance);
	\item She can travel between different locations, say her home, her workplace and and outside;
	\item She makes a different use of her devices depending on her location: her home computer will only be accessed at home, while her phone can be accessed everywhere (though she tends to use it the most at home, for instance).
\end{itemize}

We thus model each user with a Hidden Markov Model, as presented in section~\ref{sub:a_model_of_the_user_s_behavior}.
We keep the different possible locations $\mathcal{L}$ to $N=3$ and the state transition matrix $A$ to a fixed value (cf figure~\ref{fig:hmm}).
The number and types of devices per user, along with the matrix of emission probabilities $B$, is determined randomly according to the following rules.

A user always has a phone, plus a random number of 2 to 9 devices whose type is decided by a weighted random choice: each device has 30\% chances of being either mobile, portable, or fixed, and only 10\% probability of being a server.
$B_{*, d}$, the probability that device $d$ is used in each location, depends on $d$'s device type: 
\begin{itemize}
	\item for each location, every mobile device $d_m$ has a random but high probability of being online: $\forall l \in \mathcal{L}, B_{l, d_m} \in [0.6, 1]$;
	\item a portable device $d_p$ has a much lower probability of being used: $\forall l \in \mathcal{L}, B_{l, d_p} \in [0.2, 0.8]$; 
	\item a fixed appliance $d_f$ has a non-zero probability of usage in only one location: $\exists l \in \mathcal{L}, B_{l, d_f} \in [0.4, 0.8] \text{ and } \forall l' \neq l, B_{l', d_f} = 0$;
	\item a server $d_s$ has a very high probability of working, whatever the user's location: $\exists p \in [0.9, 1], \forall l \in \mathcal{L}, B{l, d_s} = p$.
\end{itemize}

@@

$$A =
\kbordermatrix{
      & W   & O   & H   \cr
    W & 0.6 & 0.4 & 0   \cr
    O & 0.2 & 0.6 & 0.2 \cr
    H & 0   & 0.4 & 0.6 \\[0.3em]
}, \;
B = 
\kbordermatrix{
      & W     & O   & H   \cr
    p & 0.7 & 0.6 & 0.8 \cr
    w & 0.7 & 0   & 0   \cr
    h & 0   & 0   & 0.7 \cr
    l & 0.2 & 0.4 & 0.6 \\[0.3em]
}$$

@@

HMMs being generative probabilistic models, they allow the generation of observation sequence $O$ given the parameters of the model $\lambda_N$.
Figure~\ref{fig:hmm} shows a possible outcome of the creation of a user's HMM, while figure~\ref{fig:sample_usage} shows an observation sequence $O$ that was generated from the displayed model.

Each round lasts $T=10s$ \commentAL{yes, the user switches places fast} and users start at different times. 
This way, even though the round's period is fixed, devices enter and leave the system at different points in the continuous time.
